Understanding Implications of Dataset Choice for Feature Effect Estimation: A Simulation-Based Investigation through Error Decomposition

### 2025-02-08 paper/paper.tex
paper: add main analysis plots

>>>>

\clearpage
\section{Additional Main Experiment Results}\label{app:additional-results}

\subsection{SimpleNormalCorrelated Dataset}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_LinReg.png}
        \caption{LinReg PDP results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_GAM_OF.png}
        \caption{GAM\_OF PDP results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_GAM_OT.png}
        \caption{GAM\_OT PDP results on SimpleNormalCorrelated}
    \end{subfigure}
\end{figure*}

\begin{figure*}[h!]
    \ContinuedFloat
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_XGBoost_OF.png}
        \caption{XGBoost\_OF PDP results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_XGBoost_OT.png}
        \caption{XGBoost\_O PDP results on SimpleNormalCorrelatedT}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_SVM_OF.png}
        \caption{SVM\_OF PDP results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_pdp_SVM_OT.png}
        \caption{SVM\_OT PDP results on SimpleNormalCorrelated}
    \end{subfigure}
    \caption{Main experiment results for PDP on SimpleNormalCorrelated dataset. $x_3$ and $x_4$ are dummy variables.}
    \label{fig:pdp-results-snc-all}
\end{figure*}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_LinReg.png}
        \caption{LinReg ALE results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_GAM_OF.png}
        \caption{GAM\_OF ALE results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_GAM_OT.png}
        \caption{GAM\_OT ALE results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_XGBoost_OF.png}
        \caption{XGBoost\_OF ALE results on SimpleNormalCorrelated}
    \end{subfigure}
\end{figure*}

\begin{figure*}[h!]
    \ContinuedFloat
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_XGBoost_OT.png}
        \caption{XGBoost\_OT ALE results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_SVM_OF.png}
        \caption{SVM\_OF ALE results on SimpleNormalCorrelated}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.67\textwidth]{img/SNC-all/feature_effect_errors_ale_SVM_OT.png}
        \caption{SVM\_OT ALE results on SimpleNormalCorrelated}
    \end{subfigure}
    \caption{Main experiment results for ALE on SimpleNormalCorrelated dataset. $x_3$ and $x_4$ are dummy variables.}
    \label{fig:ale-results-snc-all}
\end{figure*}

\clearpage
\subsection{Friedman1 Dataset}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_LinReg.png}
        \caption{LinReg PDP results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_GAM_OF.png}
        \caption{GAM\_OF PDP results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_GAM_OT.png}
        \caption{GAM\_OT PDP results on Friedman1}
    \end{subfigure}
\end{figure*}

\begin{figure*}[ht]
    \centering
    \ContinuedFloat
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_XGBoost_OF.png}
        \caption{XGBoost\_OF PDP results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_XGBoost_OT.png}
        \caption{XGBoost\_OT PDP results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_SVM_OF.png}
        \caption{SVM\_OF PDP results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_pdp_SVM_OT.png}
        \caption{SVM\_OT PDP results on Friedman1}
    \end{subfigure}
    \caption{Main experiment results for PDP on Friedman1 dataset. $x_6$ and $x_7$ are dummy variables.}
    \label{fig:pdp-results-friedman1}
\end{figure*}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_LinReg.png}
        \caption{LinReg ALE results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_GAM_OF.png}
        \caption{GAM\_OF ALE results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_GAM_OT.png}
        \caption{GAM\_OT ALE results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_XGBoost_OF.png}
        \caption{XGBoost\_OF ALE results on Friedman1}
    \end{subfigure}
\end{figure*}

\begin{figure*}[ht]
    \centering
    \ContinuedFloat
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_XGBoost_OT.png}
        \caption{XGBoost\_OT ALE results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_SVM_OF.png}
        \caption{SVM\_OF ALE results on Friedman1}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{img/Friedman1-all/feature_effect_errors_ale_SVM_OT.png}
        \caption{SVM\_OT ALE results on Friedman1}
    \end{subfigure}
    \caption{Main experiment results for ALE on Friedman1 dataset. $x_6$ and $x_7$ are dummy variables.}
\label{fig:ale-results-friedman1}
\end{figure*}

\clearpage
\subsection{Feynman I.29.16 Dataset}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_LinReg.png}
        \caption{LinReg PDP results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_GAM_OF.png}
        \caption{GAM\_OF PDP results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_GAM_OT.png}
        \caption{GAM\_OT PDP results on FeynmanI.29.16}
    \end{subfigure}
\end{figure*}

\begin{figure*}[ht]
    \centering
    \ContinuedFloat
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_XGBoost_OF.png}
        \caption{XGBoost\_OF PDP results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_XGBoost_OT.png}
        \caption{XGBoost\_OT PDP results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_SVM_OF.png}
        \caption{SVM\_OF PDP results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_pdp_SVM_OT.png}
        \caption{SVM\_OT PDP results on FeynmanI.29.16}
    \end{subfigure}
    \caption{Main experiment results for PDP on FeynmanI.29.16 dataset. $d_1$ and $d_2$ are dummy variables.}
    \label{fig:pdp-results-feynman}
\end{figure*}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_LinReg.png}
        \caption{LinReg ALE results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_GAM_OF.png}
        \caption{GAM\_OF ALE results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_GAM_OT.png}
        \caption{GAM\_OT ALE results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_XGBoost_OF.png}
        \caption{XGBoost\_OF ALE results on FeynmanI.29.16}
    \end{subfigure}
\end{figure*}

\begin{figure*}[ht]
    \centering
    \ContinuedFloat
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_XGBoost_OT.png}
        \caption{XGBoost\_OT ALE results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_SVM_OF.png}
        \caption{SVM\_OF ALE results on FeynmanI.29.16}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.86\textwidth]{img/FeynmanI.29.16-all/feature_effect_errors_ale_SVM_OT.png}
        \caption{SVM\_OT ALE results on FeynmanI.29.16}
    \end{subfigure}
    \caption{Main experiment results for ALE on FeynmanI.29.16 dataset. $d_1$ and $d_2$ are dummy variables.}
    \label{fig:ale-results-feynman}
\end{figure*}
